Artificial intelligence-assisted analysis of CT abnormalities during COVID-19 recovery

### 2024-03-22 report/markdown/report.Rmd
Report update

---
title: "Artificial inteligence-assisted analysis of CT abnormalities during COVID-19 recovery"
subtitle: "Analysis report"
author: "Piotr Tymoszuk for the Department of Radiology"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

>>>>

---
title: "Artificial intelligence-assisted analysis of CT abnormalities during COVID-19 recovery"
subtitle: "Analysis report"
author: "Piotr Tymoszuk for the Department of Radiology"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
